---
title: "Runoff Volumes"
author: "Anna Ramji"
date: "2023-08-20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## EDS 221 Day 5 Activities

### Task 1: Make a stormwater runoff estimation function, source in an Rmd

```{r}
library(tidyverse)
library(here)

```

Sourcing storm runoff script:

```{r}
source(here("src", "storm_runoff.R"))

```

-   In a code chunk in your `runoff_volumes.Rmd`, use your `predict_runoff` function to estimate stormwater volume for a watershed of 182 acres, over a range of estimates for the impervious fraction (from 0.6 to 0.8, by increments of 0.01). *Note: you do not need to write a for loop here.*

```{r}
impervious <- seq(0.6, 0.8, 0.01)

volume_ranges <- predict_runoff(impervious_frac = impervious, area = 182)
```

```{r}
stormwater_data <- data.frame(impervious_area = impervious, estimated_volume = volume_ranges)
```

```{r}
ggplot(data = stormwater_data, aes(x = impervious_area, y = estimated_volume)) +
  geom_point() +
  geom_line() +
  labs(title = "Impervious area vs. stormwater runoff volume", x = "Fraction of impervious area in watershed (unitless)", y = "Estimated stormwater runoff volume (m^3)")

ggsave(filename = here("figs", "estimated_runoff_volume.png"), width = 10, height = 6)
```
